Tables

### 2020-10-26 tables.Rmd

---
title: "Tables"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Top visited private HS (2-mode network)

```{r cars}
library(kableExtra)

df <- readRDS('./assets/tables/table_2mode.RDS')

@@

>>>>

---
title: "Tables"
output: bookdown::pdf_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(kableExtra)
library(tidyverse)
```

# Top visited private HS (2-mode network)

```{r}
df <- readRDS('./assets/tables/table_2mode.RDS')

@@

# Ego network table

```{r}
df <- readRDS('./assets/tables/table_ego.RDS')

knitr::kable(df %>% select(-Characteristics)) %>% kable_styling(latex_options = 'scale_down')
```

# Ego network graph

See Figure \@ref(fig:ego-plot).

```{r ego-plot, fig.align = 'center', out.width = '50%', fig.cap = 'Ego network'}
knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
```
